### 2024-01-17 docs/projects/noj/ml.qmd
rerendered

@@

Residuals:
       Min          1Q      Median          3Q         Max
   -0.7900     -0.2237      0.0394      0.2235      0.8037

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           1.7690     0.3120     5.6689     0.0000 ***
sepal-width         0.6801     0.0844     8.0599     0.0000 ***
petal-length        0.7043     0.0664    10.6014     0.0000 ***
petal-width        -0.5256     0.1508    -3.4858     0.0007 ***
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3057 on 96 degrees of freedom
Multiple R-squared: 0.8690,    Adjusted R-squared: 0.8649
F-statistic: 212.1968 on 4 and 96 DF,  p-value: 3.179e-42

>>>>

<div class="sourceClojure">
```clojure
(+ 2 3)
```
</div>

<div class="printedClojure">
```clojure
5

@@

Residuals:
       Min          1Q      Median          3Q         Max
   -0.7792     -0.2471      0.0207      0.2372      0.8531

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           1.6869     0.2922     5.7726     0.0000 ***
sepal-width         0.6573     0.0790     8.3247     0.0000 ***
petal-length        0.8419     0.0696    12.0977     0.0000 ***
petal-width        -0.8468     0.1618    -5.2346     0.0000 ***
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3135 on 96 degrees of freedom
Multiple R-squared: 0.8817,    Adjusted R-squared: 0.8780
F-statistic: 238.3941 on 4 and 96 DF,  p-value: 2.404e-44
